Borger et al.~\cite{Boger2002} developed a plug-in for the CASE tool ArgoUML that support UML model-based refactorings. The refactoring of class, states and activities is possible, allowing the user to apply refactorings that are not simple to apply at source code level. 
Van Gorp et al.~\cite{Gorp03towardsautomating} proposed a UML profile to express pre and post conditions of source code refactorings using Object Constraint Language (OCL) constraints. The proposed profile allows that a CASE tool: (\textit{i}) verify pre and post conditions for the composition of sequences of refactorings; and (\textit{ii}) use the OCL consulting mechanism to detect bad smells such as crosscutting concerns. In~\cite{Models2010} the authors present an approach for EMF model refactoring. They propose the definition of EMF-based refactoring in a generic way. Another approach for EMF model refactoring is presented in~\cite{ModelsEMFREfactorin}, They propose EMF Refactor~\footnote{http://www.eclipse.org/emf-refactor/}, which is a new Eclipse incubation project in the Eclipse Modeling Project consisting of three main components. Besides a code generation module and a refactoring application module, it comes along with a suite of predefined EMF model refactorings for UML and Ecore models.

The differential of our approach described herein in relation to the other is the proposal to move from software refactoring to model-driven refactoring by means of KDM, which is a platform and language independent meta-model. Furthermore, it is important to notice that the application of refactorings in UML class diagrams is not a new research as stated before. However, all of the works we found on literature perform the refactoring directly on the UML metamodel. Although UML is also an ISO standard, its primary intention is just to represent diagrams and not all the characteristics of a system.  As KDM has been created to represent all artifacts and all characteristics of a system, refactorings performed on its finer-grained elements can be propagated to higher level elements. This propitiates a more complete and manageable model-driven modernization process because all information is concentrated in just one metamodel. 

In terms of the the users who uses modernization tools like ours, the difference is not noticeable; that is, whether the refactorings are performed over UML or KDM. However, there are two main benefits of developing a refactoring catalogue for KDM. The first one is in terms of reusability. Other  modernizer engineers can take advantage of our catalogue to conduct modernizations in their  systems. The second benefit is that, unlikely UML, a catalogue for KDM can be extended to higher abstractions levels, such as architecture and conceptual, propitiating a good traceability among  these layers. 


